Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-25 WSSSPE2_report/WSSSPE2_review.tex
Section 5: touch up.

The enablers of and barriers to software sustainability, roughly ranked by
attendee votes are shown in
{\tablename}s~\ref{tb:software_sustainability_enablers} and
\ref{tb:software_sustainability_barriers}, respectively.\footnote{A few other
items were suggested as barriers, but were not voted on due to lack of time in
the session:
layering up dependencies;
using software past its sustainable life;
using software past its usable life;
inertia for accepted answers vs wrong/right answers;
monolithic or poor code; and
need to restructure code when hardware/software/libraries change.
}
\katznote{any discussion of these tables?}

\begin{table*}[ht]
 \centering
\caption{Enablers of software sustainability, with 0 to 10 `*'s roughly
indicating the fraction of attendees who voted for an item as important.}
\label{tb:software_sustainability_enablers}
  \begin{scriptsize}
  \begin{tabular}{ | p{1.65cm} | p{10.0cm} |}
   %  \begin{tabular}{ | p{1.9cm} | p{11.5cm} |}
    \hline
  Importance & Item \\ \hline \hline
********** & healthy and vibrant communities; vibrant community to champion software \\ \hline
********** & designing for growth and extension -- open development \\ \hline
******* & culture in community for reuse \\ \hline
**** & portability \\ \hline
**** & culture in dev community to support transition between developers \\ \hline
*** & interdisciplinary people: science + IT experience \\ \hline
** & planning for end of life \\ \hline
** & make smart choices about dependencies \\ \hline
* & thinking of software as product lines -- long term vs.~short term view \\ \hline
 & not all communities need new software \\ \hline
 & converting use into resources \\ \hline
    \end{tabular}
    \end{scriptsize}
\end{table*}

>>>>

The enablers of and barriers to software sustainability, roughly ranked by
attendee votes are shown in
{\tablename}s~\ref{tb:software_sustainability_enablers} and
\ref{tb:software_sustainability_barriers}, respectively.\footnote{A few other
items were suggested as barriers, but were not voted on due to lack of time in
the session:
layering up dependencies;
using software past its sustainable life;
using software past its usable life;
inertia for accepted answers versus wrong or right answers;
monolithic or poor code; and
need to restructure code when hardware/software/libraries change.
}
\katznote{any discussion of these tables?}

\begin{table*}[ht]
 \centering
\caption{Enablers of software sustainability, with 0 to 10 `*'s roughly
indicating the fraction of attendees who voted for an item as important.}
\label{tb:software_sustainability_enablers}
  \begin{scriptsize}
  \begin{tabular}{ | p{1.65cm} | p{10.0cm} |}
   %  \begin{tabular}{ | p{1.9cm} | p{11.5cm} |}
    \hline
  Importance & Item \\ \hline \hline
********** & healthy and vibrant communities; vibrant community to champion software \\ \hline
********** & designing for growth and extension -- open development \\ \hline
******* & culture in community for reuse \\ \hline
**** & portability \\ \hline
**** & culture in development community to support transition between developers \\ \hline
*** & interdisciplinary people: science + IT experience \\ \hline
** & planning for end of life \\ \hline
** & make smart choices about dependencies \\ \hline
* & thinking of software as product lines -- long term vs.~short term view \\ \hline
 & not all communities need new software \\ \hline
 & converting use into resources \\ \hline
    \end{tabular}
    \end{scriptsize}
\end{table*}
